---
title: "DS_FinalProject"
author: "peteryu"
date: "2018/1/8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('scales')
library('dplyr') 
library('randomForest') 
library('methods')
library('argparser')
library('caret')
library('Hmisc')
library('e1071')
library('corrplot')
```

## Occupancy detection using UCI ML repository dataset.

This is the final project from Data Science class @ NCCU CS.

Our target is to find out if the office is availabel for use from this dataset.

### Data loading

First, load dataset from './occupancy_data'.

```{r data loading}
train <- read.csv('./occupancy_data/train.csv', stringsAsFactors = F)
test1 <- read.csv('./occupancy_data/test1.csv', stringsAsFactors = F)
test2 <- read.csv('./occupancy_data/test2.csv', stringsAsFactors = F)
```

In training data, there are total 8144 rows. 

In testing data, there are 12416 rows.

Here only shows a few rows from those data.

There are seven attributes collecting from sensor inside the office.

No missing data is this dataset.

```{r train}
head(train)
```
```{r test}
head(test1)
```

###Data preprocessing

Now, we need to do some data preprocessing. 

Combine training and testing data.
Since 'Date' is time serial, we want some categorical attributes, so convert it into Weekdays and Time.

```{r preprocessing}
full <- bind_rows(train, test1, test2)
full$Weekdays <- sapply(full$Date, function(x) if(weekdays(as.Date(strsplit(x, " ")[[1]][1])) == '週六' || weekdays(as.Date(strsplit(x, " ")[[1]][1])) == '週日') 'weekend' else 'weekday')
full$Time <- sapply(full$Date, function(x) if(strsplit(x, " ")[[1]][2] < '12:00' && strsplit(x, " ")[[1]][2] > '00:00') 'morning' else if(strsplit(x, " ")[[1]][2] > '18:00') 'evening' else 'afternoon')

head(full)
```

Preprocessing is done, split dataset into training and testing data.

We don't need 'Date' attribute for model construction, so here we use dataset from column index 2.

```{r split data}
train <- full[1:8144, 2:9]
test <- full[8145:20560, 2:9]
```

For further model comparsion, we generate two list with all prediction of zero(vacant), and one(occupy).

```{r null model, echo=FALSE}
null_list <- c()
one_list <- c()

for(i in c(1:12416)){
  null_list <- c(null_list, 0)
  one_list <- c(one_list, 1)
}

head(null_list)

head(one_list)
```

Summary about training and testing data.

```{r summary}
train$Occupancy <- as.factor(train$Occupancy)
test$Occupancy  <- as.factor(test$Occupancy)

summary(train)

summary(test)
```

Plotting the correlation about attribute of training data.

```{r corr, echo=FALSE}
correlation_result<-rcorr(as.matrix(train[2:6]))
corrplot(correlation_result$r,type="upper", order="hclust", tl.col="black", tl.srt=45)
```

###Model Construction

Constructing our supervised learning model using random forest classifcation algorithm.

Underneath shows each attribute importance during decision tree classifier constructing.

```{r rf}
set.seed(1234)
model_all <- train(Occupancy~.,method="rf",data=train)
plot(varImp(model_all,scale=TRUE))
```

Finally, the accuracy of this model compare two null model.

```{r acc, echo=FALSE}
rf_acc <- sum(test$Occupancy==predict(model_all,test))/dim(test)[1]*100
zero_acc <- sum(test$Occupancy==null_list)/dim(test)[1]*100
one_acc <- sum(test$Occupancy==one_list)/dim(test)[1]*100
  
m <- c("Random Forest", "null model-0", "null model-1")
acc <- c(rf_acc, zero_acc, one_acc)
acc_table <- data.frame(Model=m,
                        Accuracy=acc,
                        stringsAsFactors = F)
acc_table
```

The confusion matrix.

```{r cm, echo=FALSE}
set.seed(1234)
confusionMatrix(test$Occupancy,predict(model_all,test))
```